Periodograms for Multiband Astronomical Time Series

### 2015-01-30 writeup/paper.tex
fixed two typos in sec 7.1

Computationally, the PGLS model requires a nonlinear optimization at each frequency $\omega$, and is thus much more expensive than the straightforward linear optimization of our shared-phase model.
For this reason, LCB14 propose a clever method by which nested models are used to reduce the number of nonlinear optimizations used: essentially, by showing that the (linear) MGLS $\chi^2$ is a lower-bound of the (non-linear) PGLS $\chi^2$, it is possible to iteratively reduce the number of PGLS computations required to minimize the $\chi^2$ among a grid of frequencies.
Such an optimization could also be applied in the case of our shared-phase model, but is not necessary here due to its relative speed.
When applying the method to a very large number of light curves in, e.g. LSST however, such a computational trick may prove very useful.

>>>>

Computationally, the PGLS model requires a nonlinear optimization at each frequency $\omega$, and is thus much more expensive than the straightforward linear optimization of our shared-phase model.
For this reason, LCB14 propose a clever method by which nested models are used to reduce the number of nonlinear optimizations used: essentially, by showing that the (linear) MGLS $\chi^2$ is a lower-bound of the (non-linear) PGLS $\chi^2$, it is possible to iteratively reduce the number of PGLS computations required to minimize the $\chi^2$ among a grid of frequencies.
Such an optimization could also be applied in the case of our shared-phase model, but is not necessary here due to its already high speed.
However, when applying the method to a very large number of light curves, as in e.g. LSST, such a computational trick may prove very useful.
